---
title: "Macedonian syllable structure"
author: "K. Romanova"
date: "October 2, 2018"
bibliography: bibliography.bib
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

## Македонский язык  

< Macedo-Bulgarian < Eastern South Slavic < South Slavic < Slavic < Balto-Slavic < Indo-European  
Официальный статус: Республика Македония (государственный язык), ... 

## Фонетика 

<таблица>  
? таблица с гласными 

## Описание слоговой структуры 

инициаль — ядро — финаль 
* инициаль — согласные, предшествующие ядру  
* финаль — согласные, следующие за ядром 
* ядро — вершина слога 

## Принципы слогоделения 



## Intro

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with bibliography

В работе [@heeringa15]...

## Bibliography
